### 2022-03-23 rmd/suppl_info.Rmd
Update suppl_info.Rmd

@@

```{=tex}
\newpage
\pagenumbering{arabic}
```

@@

@@

  table_legend <- paste0("Sensitivity analysis of the ", c_text[i]," effect on the FCL. Parameter estimates of linear regression models are shown. The response variable is the Spearman's rank correlation between food chain length and ", c_text[i],". Response and explanatory variables (i.e., simulation parameters) were standardized (mean = 0, SD = 1) before the analysis.")

@@

  figure_legend <- paste0(str_to_sentence(c_text[i])," effect on food chain length. We used the following values of parameters: $\\theta$ = `r df_sim$theta[i]`, $\\sigma_l$ = `r df_sim$sd_disturb_lon[i]`, and $\\sigma_h$ = `r df_sim$sd_disturb_source[i]`")

  knit_chunk <- paste0("## Figure S", i + j, " ", str_to_sentence(c_text[i]), " effect on food chain length", " \n",
                       "\n```{r figure_s", i + j,", fig.height = 6.5, fig.width = 8}
                       \n\n
                       list_g_fcl[[", i,"]]
                       \n\n
                       ```\n",
                       figure_legend,
                       "\n\\pagebreak\n")

>>>>

options(knitr.kable.NA = '')

@@

```{=tex}
\newpage
\pagenumbering{arabic}
```
## Table S1 Parameter values

Parameter values used for the main and sensitivity analysis.

```{r table_param}

source(here::here("code/table_param.R"))
knitr::kable(df_value, format = "markdown")

@@

j <- 1

@@

  table_legend <- paste0("Sensitivity analysis of the ", c_text[i]," effect on food chain length. Parameter estimates of linear regression models are shown. The response variable is the Spearman's rank correlation between food chain length and ", c_text[i],". Response and explanatory variables (i.e., simulation parameters) were standardized (mean = 0, SD = 1) before the analysis.")

@@

  K <- length(list_g_fcl[[i]])

  for(k in 1:K) {

      figure_legend <- paste0(str_to_sentence(c_text[i])," effect on food chain length and occupancies of constituent species. Lines and shades represent loess curves fitted to the simulated data and 95% confidence intervals. In this simulation, the following values of parameters were used: $\\theta$ = ", df_param$theta[k], ", $\\sigma_l$ = ", df_param$sd_disturb_lon[k], ", and $\\sigma_h$ = ", df_param$sd_disturb_source[k], ".")

  knit_chunk <- paste0("## Figure S", K * (i - 1) + k + j, " ", str_to_sentence(c_text[i]), " effect on food chain length", " \n",
                       "\n```{r figure_s", K * (i - 1) + k + j,", fig.height = 10, fig.width = 11.5}
                       \n\n
                       list_g_fcl[[", i, "]][[", k, "]]
                       \n\n
                       ```\n",
                       figure_legend,
                       "\n\\pagebreak\n")
